# Graph Problems

## Maximum weight matching

### Introduction and Setting

To quote [Wikipedia](https://en.wikipedia.org/wiki/Maximum_weight_matching):

> In computer science, the maximum weight matching problem is the problem of finding, in a weighted graph, a matching in which the sum of weights is maximized.

Our setting is a weighted, undirected graph $G=(V,E)$ and we are interested in
finding a subset of edges such that the set is a [matching](https://en.wikipedia.org/wiki/Matching_(graph_theory)) (i.e. no
two edges share the same vertex) and the sum of the weights is maximal.

We will use the igraph package to construct a sample graph:

```{r}
library(igraph)
set.seed(123)
graph <- make_graph("House")
E(graph)$weight <- rpois(ecount(graph), lambda = 5)
plot(graph, edge.label = E(graph)$weight)
```

### The model and solution

```{r}
library(rmpk)
library(ROI.plugin.glpk)
# we start with an empty model and GLPK as the solver
# TODO: cite a good book/paper regarding the problem and add a proper latex description of the problem
# In the meatime, please refer to https://www.arl.wustl.edu/~jst/cse/542/text/sec15.pdf
# or https://cs.stackexchange.com/questions/104017/maximum-matching-using-linear-programming
# for more information/references
model <- optimization_model(ROI_optimizer("glpk", control = list(verbose = TRUE)))

# for each edge we define a 0-1 variable that indicates if the edge is part
# of the matching or not.
x <- model$add_variable("x", edge = E(graph), type = "binary")

# now we maximise the sum of the weight of all selected edges
weight <- E(graph)$weight
model$set_objective(
  sum_expr(weight[edge] * x[edge], edge = E(graph)),
  sense = "max"
)

# at last we need to make sure that each vertex is only connected to at most
# 1 edge. I.e. the sum of selected edges incident to a given vertex cannot be
# larger than 1.
model$add_constraint(
  sum_expr(x[edge], edge = incident(graph, vertex)) <= 1, 
  vertex = V(graph)
)

model$optimize()
```
```{r}
(solution <- model$get_variable_value(x[edge]))
```

And now we can plot the provable, optimal solution with objective value `r model$objective_value()`:

```{r}
selected_edges <- solution[solution$value == 1, ]$edge
color <- rep.int("black", ecount(graph))
color[selected_edges] <- "red"
E(graph)$color <- color
plot(graph, edge.label = E(graph)$weight)
```

