--- 
title: "Practical Discrete Optimization in R: A Cookbook"
author: "Dirk Schumacher"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
bibliography: [book.bib, packages.bib]
github-repo: r-opt/cookbook
documentclass: book
description: "A work-in-progress cookbook on {rmpk}."
---

# Introduction And Setup

The goal of this book is to compile a list of practical Operations Research problems that can be solved with `rmpk`. During initial package development it acts as early documentation and also a big integration test to guide further development.

It currently is assumed you already know a bit about the theory of mixed integer programming (I will write something about it at a later point in time).

Each chapter is a broad problem category (like Scheduling or Puzzles) and contains a set of problems that help you get started.

In order to run the examples in this book, you need the `rmpk` package together with a solver.

```{r eval=FALSE}
options(repos = c(
    ropt = "https://r-opt.r-universe.dev",
    CRAN = "https://cloud.r-project.org"))

install.packages("rmpk") # modelling
install.packages("ROIoptimzer") # ROI optimizer
install.packages("ROI.plugin.glpk") # Bindings to GLPK
```

**Please note however that this book is work in progress. So there will be typos, mistakes, missing/wrong references, unfinished sections, etc.**

License:
Attribution-NonCommercial-ShareAlike 4.0 International (CC BY-NC-SA 4.0)
https://creativecommons.org/licenses/by-nc-sa/4.0/

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
